---
title: "Simulate correlated and ordered categorical data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Simulate correlated and ordered categorical data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fatcat)
```

The fat cat package provides two ways for simulating ordered categorical data. We start by setting the true values of the parameters.

```{r example}
j <- 5
n <- 300
k <- 4
true_p <- 2

true_beta <- matrix(
  c(
    0.99, 0.00,
    0.00, 0.99,
    0.90, 0.00,
    0.00, 0.90,
    0.50, 0.50
  ),
  nrow = j, ncol = true_p,
  byrow = TRUE
)

true_sigma <- c(0.01, 0.05, 0.10, 0.15, 0.20)

true_alpha <- matrix(
  c(-Inf, qnorm(0.4), qnorm(0.75), qnorm(0.9), Inf),
  nrow = j, ncol = (k + 1),
  byrow = TRUE
)
```

One of the ways of generating data is using the marginal model, which can be achieved with the following:

```{r}
y_marginal <- simulate_data(beta = true_beta, sigma = true_sigma, alpha = true_alpha, n = n, link = "probit")
```


Alternatively, the data can be simulated using the full model, and thus we need to have an additional "parameter", the latent factors.

```{r}
true_f <- t(
  MASS::mvrnorm(n, rep(0, true_p), diag(1, true_p, true_p))
)

y_full <- simulate_data(true_beta, true_sigma, true_alpha, f = true_f, link = "probit")
```

Both methods are equivalent. Note that variables 1 and 3 are highly correlated. The same happens for variables 2 and 4.

```{r}
cor_full <- psych::polychoric(t(y_full))$rho
cor_marginal <- psych::polychoric(t(y_marginal))$rho

par(mfrow= c(1,2))
corrplot::corrplot(cor_full, type = "upper") 
corrplot::corrplot(cor_marginal, type = "upper")
```
